Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Title, conclusions

\title{Large scale agile transformations: A literature review}

\titlerunning{Large scale agile transformations}

@@

\institute{Aalto University . . . Address . . .
\\ \email{email@xx},
\\ WWW home page: \texttt{http://www...} }

@@

\begin{abstract}        % give a summary of your paper
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%                         please supply keywords within your abstract
\keywords {agile, transformation, large scale}
\end{abstract}

@@

This paper is organized as follows. The next section gives an overview of large
scale agile development. Section \ref{sec:method} presents the literature review
method used for conducting the research. The findings of the review are
discussed in section \ref{sec:results}, and section \ref{sec:conclusions}
discusses the findings and gives proposals for future research.

@@

% ---------------------------------------------------------------------
\section{Conclusions}
\label{sec:conclusions}

* -- Research on large scale agile transformations has been published.

-- Papers presenting the effect of agile on specific areas in software
development exist, but the whole has not been studied as much.

\subsection{Limitations}

@@

\subsection{Future research}

* -- Very little studies on quantitative comparison of before/after transformation
has been done. (how about quantitative?)

-- What thihgs are important to report in an agile transformation case study?

-- Do not focus exclusively on the software perspective, but find parallels from
general research on organizaional transformation and leadership. (Tähän pitäs
vissiin sitte olla joku konkreettinen ehdotus?)

@@

Otsikko:
literature review -> motivation, success and challenges

@@

\begin{supertabular}{ l p{11.3cm} }
    {[}S1{]} & \bibentry{S1} \\ \shrinkheight{-2.1cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\ 
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\ 
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}

>>>>

\title{Adopting agile in the large: motivations, success factors and challenges}

\titlerunning{Adopting agile in the large}

@@

\institute{Aalto University . . . Address . . .
\\ \email{kim.dikert@aalto.fi}, \email{maria.paasivaara@aalto.fi} }

@@

\begin{abstract}        % give a summary of your paper
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%                         please supply keywords within your abstract
\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

@@

This paper is organized as follows. The next section gives an overview of large
scale agile development. Section \ref{sec:method} presents the literature review
method used for conducting the research. The findings of the review are
discussed in section \ref{sec:results}, and section \ref{sec:conclusion}
gives proposals for future research.

@@

% ---------------------------------------------------------------------
\section{Future research}
\label{sec:conclusion}

Our results show that a body of research on large scale agile transformations
has emerged. We aim to continue research on this topic by conducting a
systematic literature review. Beyond descriptive reports on agile
transformations we found very little studies with quantitative comparison of
organizations before and after the transformations.

@@

@@

@@

\begin{supertabular}{ l p{11.4cm} }
    {[}S1{]} & \bibentry{S1} \\ \shrinkheight{-1.6cm}
    {[}S2{]} & \bibentry{S2} \\ 
    {[}S3{]} & \bibentry{S3} \\ 
    {[}S4{]} & \bibentry{S4} \\ 
    {[}S5{]} & \bibentry{S5} \\ 
    {[}S6{]} & \bibentry{S6} \\ 
    {[}S7{]} & \bibentry{S7} \\ 
    {[}S8{]} & \bibentry{S8} \\ 
    {[}S9{]} & \bibentry{S9} \\ \shrinkheight{-1.6cm}
    {[}S10{]} & \bibentry{S10} \\ 
    {[}S11{]} & \bibentry{S11} \\ 
    {[}S12{]} & \bibentry{S12} \\ 
    {[}S13{]} & \bibentry{S13} \\ 
    {[}S14{]} & \bibentry{S14} \\ 
    {[}S15{]} & \bibentry{S15} \\ 
    {[}S16{]} & \bibentry{S16} \\ 
    {[}S17{]} & \bibentry{S17} \\ 
    {[}S18{]} & \bibentry{S18} \\ 
    {[}S19{]} & \bibentry{S19} \\ 
    {[}S20{]} & \bibentry{S20} \\ 
    {[}S21{]} & \bibentry{S21} \\ 
    {[}S22{]} & \bibentry{S22} \\ 
    {[}S23{]} & \bibentry{S23} \\ 
    {[}S24{]} & \bibentry{S24} \\ 
    {[}S25{]} & \bibentry{S25} \\ 
    {[}S26{]} & \bibentry{S26} \\ 
    {[}S27{]} & \bibentry{S27} \\ 
    {[}S28{]} & \bibentry{S28} \\ 
    {[}S29{]} & \bibentry{S29} \\ 
    {[}S30{]} & \bibentry{S30} \\ 
\end{supertabular}\end{document}
